---
title: 'STAT 118: Notes K'
subtitle: 'Maps with `maps` and `sf`'
format:
  html:
    toc: true
    code-overflow: wrap
---

### Before we get started, some context:

- `R` is ***fantastic*** for spacial analysis (not covered in this class... look for classes related to spacial statistics)
- `R` is *great* for interactive data visualization (via `leaflet` or `shiny`... more on this on Thursday)
- `R` is *okay* at spacial data visualization (creating maps).
  - There are many different packages in `R` for creating maps. I've found that different packages perform best for different maps. We will talk about a few different ones today. 
  -  If you have a highly map-centric project, there is nothing wrong with working in ArcGIS or QGIS if you find the mapping tools in R insufficient. There are many recent improvements with new packages (like `sp`, `rgdal` and `rgeos`) which profiles much of the functionality of GIS packages! Exciting! (not very beginner friendly - requires familiarity with GIS concepts)

# Using the `maps` package

Perhaps the simplest approach to drawing maps is to use `geom_polygon()` to draw boundaries for different regions.

The `maps` package contains several built in maps: world (for all countries in the world), france, italy, nz, usa, state (usa state boundaries), and county (usa counties). The maps package isn’t particularly accurate or up-to-date, but it’s built into R so it’s an easy place to start.

To reference each map you use `map_data("mapname")`. 

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES
library(tidyverse)
library(maps)

#LOAD DATA
world_map <- map_data("world")
```

```{r}
#World Map
ggplot(world_map, aes(long, lat, group=group)) + 
  geom_polygon() +
  coord_quickmap()
```

Note:

- `coord_quickmap()` adjusts the axes to ensure that longitude and latitude are rendered on the same scale. It is very important that this aspect ratio is maintained or a country may appear super stretched or super squished.
- the `aes(group=group)` option -- This is SUPER IMPORTANT, so R knows which things to connect together

## What about subsetting the data? 

```{r}
#Subset to get Italy
italy <- map_data("world", region ="Italy")

#Subset to get USA
usa <- map_data("world", region ="USA")
```


## What if aspect ratio is not maintained? 

```{r}
# ASPECT RATIO NOT MAINTAINED
ggplot(italy, aes(long, lat)) + 
  geom_polygon(aes(group=group)) + 
  theme_light() +
  ggtitle("Italy - Aspect Ratio Not Maintained (not good)")
```

```{r}
# ASPECT RATIO MAINTAINED
ggplot(italy, aes(long, lat)) + 
  geom_polygon(aes(group=group)) + 
  coord_quickmap()  +
  theme_light() +
  ggtitle("Italy - Aspect Ratio Maintained (better)")
```

## USA with states

```{r}
#Load Data from maps
usa_states <- map_data("state")

#Plot of USA with state borders

```


## How to customize colors? 

```{r}

```



# Using the `sf` package

here are a few limitations to the approach outlined above, not least of which is the fact that the simple "longitude-latitude" data format is not typically used in real world mapping. Vector data for maps are typically encoded using the "simple features" standard produced by the Open Geospatial Consortium. The `sf` package developed by Edzer Pebesma provides an excellent toolset for working with such data, and the `geom_sf()` and `coord_sf()` functions in ggplot2 are designed to work together with the `sf` package.

```{r}
#LOAD PACKAGES
#install.packages("sf") - note some students are getting a pop-up when they install the sf package for the first time. Select the "no" option when it pops up in your console. 
library(sf)

#some students are needing into install the rgeos package seperately as well
#library(rgeos)
```

For our first example, we will be working with a dataset of North Carolina that is built in to the `sf` package.

```{r}
demo(nc, ask = FALSE, echo = FALSE)
```

You should notice that the `nc` dataset is now saved in your R environment. This dataset contains information about Sudden Infant Death Syndrome (SIDS) for North Carolina counties, over two time periods (1974-78 and 1979-84). Let’s take a look at that dataset.

Each row represents a county in North Carolina. This data frame contains the following columns:

- `AREA` County polygon areas in degree units
- `PERIMETER` County polygon perimeters in degree units
- `CNTY_` Internal county ID
- `NAME` County names
- `FIPS` County ID
- `FIPSNO` County ID
- `CRESS_ID` Cressie papers ID
- `BIR74` births, 1974-78
- `SID74` SID deaths, 1974-78
- `NWBIR74` non-white births, 1974-78
- `BIR79` births, 1979-84
- `SID79` SID deaths, 1979-84
- `NWBIR79` non-white births, 1979-84
- `geom` information needed to plot the map for each county

Let's begin by simply plotting the map: 

```{r}

```


Let's pretty it up: 

```{r}

```



## Cloropleth maps

Suppose we want to shade each of these counties, based on the number of births in 1974. 

This is called a "cloropleth" map (a map that uses differences in shading, coloring, or the placing of symbols within predefined areas to indicate the average values of a property or quantity in those areas). 

```{r}

```


Here are some options to customize the plot that you might be interested in: 



### Using RColorBrewer palette

```{r}
library(RColorBrewer)


ggplot(nc) + 
  geom_sf() + 
  aes(fill = BIR74) +
  ggtitle("North Carolina, Birth Rates in 1974") +
  
  theme_light()
```


### Using part of a RColorBrewer palette

```{r}

ggplot(nc) + 
  geom_sf() + 
  aes(fill = BIR74) +
  ggtitle("North Carolina, Birth Rates in 1974") +
  
  theme_light()
```


### Building your own color palette using `scale_fill_gradientn`

```{r}

ggplot(nc) + 
  geom_sf() + 
  aes(fill = BIR74) +
  ggtitle("North Carolina, Birth Rates in 1974") +

  theme_light()
```


A note about customizing colors:

- you should use a color scheme that is sequential (has order to it), when you are displaying continuous data
- you should use a color scheme that is categorical, when your data is in categories and isn’t ordered
you should use a color scheme that is diverging, when want to put emphasis on two extremes and mid-range. For example, you might use a diverging palette from red to blue for political party affiliation in the US.
- pay attention to your map being color blind friendly (RdYlGr is the worst…)
- as a general rule, try not to use blue to represent a land mass (let’s reserve that for bodies of water)


## Adding labels

```{r}
 
ggplot(nc) + 
  geom_sf() + 
  aes(fill = BIR74) +
  ggtitle("North Carolina, Birth Rates in 1974") +
  scale_fill_gradientn(colors = brewer.pal(8, "Spectral") ) +  #customize colors
  theme_light() 
```

