---
title: "Math 118: Notes Q"
subtitle: "Introducing Stringr"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

# A few basics

**What is a string?**



###Examples of strings:



###NOT a string:




**What is stringr?**
stringr is a package containing a bunch of functions that help us work with strings.
  
[**stringr cheat sheet**](https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_strings.pdf)

# Using `stringr`

**I'm registering for classes this Fall and am trying to decide what to take.**
Let's look at the course catalog!

Read in the courses data.
```{r, message=FALSE, warning=FALSE}
courses <- read_csv("Fall23courses.csv")
```
  
  
    
## `str_detect` 
  
**inputs**: - 
            - 
**output**: 

little example:
```{r}

```



I only want to take classes in Warner! 
```{r}

```
  
  
  
Suppose I don't want any classes on Friday. Let's use `str_detect` to find our options.
```{r}

```


Perhaps I'm interested in artificial intelligence.  
 
  
The `regex` function is used to write regular expressions in R. Regular expressions are helpful if you want to search for a pattern rather than a specific word or phrase.  
For now, we will only use regex to ignore capitalization. 
If you're interested in using regular expressions at some point, this [regex cheat sheet](https://cheatography.com/davechild/cheat-sheets/regular-expressions/) will be super helpful.

```{r}


```
  
  
  
## `str_extract` and `str_remove`
  
  
**str_extract inputs**: - 
            - 
**str_extract output**:  

**str_remove inputs**: - 
            - 
**str_remove output**:  

little example:
```{r}

```
  
  
  
CW is part of the distribution requirement column. I want CW to be its own column.  
```{r}

```
  
  
  
## `str_sub`
  
  
**str_sub inputs**: -    
            -  
            -  
**str_sub output**:     
  
little example:
```{r}

```
  

Maybe I only want 200 level math classes.  
First we filter for just math classes. 


```{r}

```
  
  
  
## `str_count`
  
  
little example:
```{r}

```
 
  
**str_count inputs**: -    
            -    
**str_count output**: 


Maybe I only want my classes to meet twice a week.
```{r}


#what's the maximum number of days a week a class meets?


#what's the mean number of days?

```

Let's visualize this data.
```{r}


```
