---
title: "STAT 118: Homework E"
subtitle: "Making plots  with ggplot2: histograms, boxplots, jitter, labels"
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r}
#LOAD PACKAGES 
library(tidyverse)
```

To the best of your ability, recreate the following plots from the penguins dataset. Focus your efforts on getting the content correct. If you have time at the end, as a bonus, you can try to match the styling as closely as you can.

This image will also be available on the Canvas assignment (in case this link/preview don't work for you). 

# 1. Iris Side-by-Side Boxplot

```{r}
#load the iris dataset
data("iris")
```


```{r}

```

# 2. Gapminder Barplot

```{r}
#load the gapminder dataset
library(gapminder)
data("gapminder")
```


```{r}

```

# 3. Gapminder Line Graph

```{r}
library(tidyverse)
library(ggthemes) # you might need this to help with the theme... 
```


```{r}

```

# 4. Penguins Histogram

```{r}
#Load Penguins Data
library(palmerpenguins)
data("penguins")
```

```{r}

```
