---
title: "STAT 118: Homework"
subtitle: 'Plotting Points on Maps'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(sf) 
library(leaflet)
library(spData)
```

Choose one of the datasets provided which displays the latitude and longitude of many locations. Your job will be to create a map which displays the locations of the items on an appropriate map.

- Dunkin Donuts Locations 
https://github.com/emalcolmwhite/emalcolmwhite.github.io/blob/main/courses/stat0118/data/dunkin_stores.csv
- Farmers Markets in the USA https://github.com/emalcolmwhite/emalcolmwhite.github.io/blob/main/courses/stat0118/data/farmers_markets_from_usda.csv


# 1.
Use the space below to import in your dataset of choice 

**Keep in mind that you may want to work with ALL locations in the dataset OR you may wish to work with a subset of the locations -- totally your choice.**

```{r}

```

# 2.
Find an appropriate `sf` dataset for the locations of your data. Recall the `spData` package contains many different `sf` objects, so you might be able to find an appropriate map there. 

```{r}

```

# 3.
Create an `ggplot` map (using `sf` objects) which displays the locations from your dataset as points on the map. All points should be the same size (choose an appropriate size and color). Your plot should include a title and appropriate colors. 

```{r}

```

# 4.
Create an `ggplot` map (using `sf` objects) which displays the locations from your dataset as points on the map. Your points should vary in size depending on a quantitative variable in your data OR vary in color depending on a categorical variable in your data. Your plot should include a title and appropriate colors.

```{r}

```

# 5.
Create a `leaflet` map which displays the locations from your dataset as well-labeled markers on a map. 

```{r}

```

