---
title: 'Plotting Points on Maps'
author: 'Emily Malcolm-White'
format:
  html: 
    toc: TRUE
    code-overflow: wrap
    embed-resources: true
    code-tools:
      source: true
      toggle: false
      caption: none
    code-annotations: hover
execute: 
  message: FALSE
  warning: FALSE
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(sf) #this is a package needed so R can work with sf objects

#LOAD DATA
library(spData) #this packages contains the dataset (with sf objects) that we will be using today
data("us_states")
```

# More `sf` maps with points

Recall our map of the continential US which shows the state borders. 

```{r}
us_states %>% 
ggplot() + 
  geom_sf() +
  theme_light()
```

Recall the `nycflights13` dataset which had all kinds information about all the flights out of NYC airports in 2013. Check out the `airports` dataset, which has the latitude and longitude of all airports in the USA. 

```{r}
library(nycflights13)
data(airports)
```

Suppose we want to plot these onto our map: 

```{r}
us_states %>% ggplot() +
geom_sf() +
theme_light() + geom_point(data=airports, aes(x=lon, y=lat), pch=19, size=0.1) +
  coord_sf(xlim = c(-130, -65),ylim = c(20,50))
```

What if we wanted to have each dot size represent the number of flights that flew to those airports from NYC? First we need the data: 

```{r}
data(flights)

dest_count <- flights %>%
  group_by(dest) %>%
  summarize(count=n())
```

Then we need to merge this data into the `airports` dataset: 

```{r}
airports_count <- airports %>%
  inner_join(dest_count, by=c("faa"="dest"))
```

Then we can add it to our plot: 

```{r}
library(scales)

us_states %>%
  ggplot() +
  geom_sf() +
  theme_light() +
  geom_point(data = airports_count, aes(x = lon, y = lat, size = count)) +
  scale_size(
    range = c(0.2, 5),
    breaks = c(0, 1, 10, 100, 1000, 10000, 100000),
    labels = comma  # 👈 this formats labels with commas (e.g., 10,000)
  ) +
  coord_sf(xlim = c(-130, -65), ylim = c(20, 50))
```


# Leaflet

Leaflet is one of the most popular open-source JavaScript libraries for interactive maps. 

```{r}
library(leaflet)
```

You create a Leaflet map with these basic steps:

1. Create a map widget by calling leaflet().
2. Add layers (i.e., features) to the map by using layer functions (e.g. `addTiles`, `addMarkers`, `addPolygons`) to modify the map widget.
3. Repeat step 2 as desired.

## Using OpenStreet Maps

A simple map of Warner Hall: 

```{r}
leaflet() %>%
  addTiles() %>%  
  # Add default OpenStreetMap map tiles
  addMarkers(lng=-73.175, lat=44.010, popup="Warner Hall")
```

A map of all airports in the USA: 

```{r}
leaflet(data=airports_count) %>%
  addTiles() %>% # Add default OpenStreetMap map tiles
  addMarkers(lng=~lon, lat=~lat, popup=~faa)
```

or using Circle Markers: 

```{r}
leaflet(data=airports_count) %>%
  addTiles() %>%# Add default OpenStreetMap map tiles
  addCircleMarkers(lng=~lon, lat=~lat, popup=~faa, radius = ~count/1000, stroke =FALSE, fillOpacity =0.5)
```


