---
title: "STAT 118: Homework F"
subtitle: 'Making plots  with `ggplot2`: line graphs, histograms & boxplots'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)

#Load Penguins Data
library(palmerpenguins)
data("penguins")
```

To the best of your ability, recreate the following plots from the penguins dataset. Focus your efforts on getting the content correct. If you have time at the end, as a bonus, you can try to match the styling as closely as you can.

This image will also be available on the Canvas assignment (in case this link/preview don't work for you). 

# 1. Iris Side-by-side Boxplot

```{r}
#load the iris dataset
data("iris")
```

![]()

```{r}

```

# 2. Gapminder Histogram

```{r}
#load the gapminder dataset
library(gapminder)
data("gapminder")
```

![]()

```{r}
gapminder %>% 
  filter(continent == "Europe" & year == "1952") %>% 
  ggplot(aes(x=lifeExp)) +
  geom_histogram(fill = "cornflowerblue", col="black", binwidth=3) +
  ggtitle("Distribution of Life Expectancy of \n European Countries in 1952") + 
  xlab("Life Expectancy") +
  theme_void() +
  theme(axis.title.x = element_text(),
        axis.text.x = element_text(),
        panel.grid.major.y = element_line("grey"),
        panel.grid.minor.y = element_line("grey")) 
```

# 3. Gapminder Line Graph

![]()

```{r}

```

# 4. Penguins Scatterplot

```{r}
#Load Penguins Data
library(palmerpenguins)
data("penguins")
```

![]()

```{r}

```
