---
title: "STAT 118: Homework O"
subtitle: 'Webscraping Tables'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r, warning=FALSE, message=FALSE}
#make sure the package is installed on your computer or this won't run! 
library(tidyverse)
library(rvest)
```

# 1. 
Use `read_html` to read in all the HTML code from [Middlebury Colleges's wikipedia page](https://en.wikipedia.org/wiki/Middlebury_College). Save this HTML code as `Midd_html`

```{r}
Midd_html <- read_html("https://en.wikipedia.org/wiki/Middlebury_College")
```


# 2. 
Use the appropriate code to save the 1st table on this wikipedia page as a tibble in R with the name `Midd_Table1`. Don't worry about cleaning it up. 

```{r}
Midd_Table_1 <- Midd_html %>% 
  html_element("table") %>% 
  html_table()
```


# 3. 
Use the appropriate code to save the ALL the tables on this wikipedia page as `Midd_Tables`. Don't worry about cleaning it up. 

```{r}

```

# 4. 
Use the appropriate code to scrape the [Admission Statistics table in the Admissions section](https://en.wikipedia.org/wiki/Middlebury_College#Admissions). Save this table as tibble named `Midd_Admissions`



```{r}
Midd_Admissions <- Midd_html %>% 
  html_element(".wikitable") %>% 
  html_table()
```

# 5. 

Use `Midd_Admissions` you create above to recreate the following table below which shows the number of Applicants, Admits, and Enrolled in each year. *Hint: You may need to revisit our lesson on pivoting!* 

	year	Applicants	Admits	Enrolled
	2023	13,297	1,462	630
	2022	13,028	1,955	640
	2021	11,906	1,601	680
	2020	9,174	2,022	602
	2019	9,754	1,498	605
	2018	9,227	1,542	628
	2017	8,909	1,523	635
	2016	8,819	1,423	606
	2015	8,891	1,551	589
	2014	8,195	1,407	580
	2013	9,109	1,595	625
	
It is totally okay if your years are not displaying properly. For example, `2023` may display as `2023_74` or `x2023_74` or something similar. You don't need to fix this in order to get full marks. If you are feeling up for a challenge, you could check out `stringr::str_sub` as a way to fix this.  
	

```{r}
# library(janitor)
# Midd_Admissions %>% 
#   clean_names() %>% 
#   pivot_longer(2:12, names_to = "year", values_to="number") %>% 
#   filter(x %in% c("Applicants", "Admits", "Enrolled")) %>% 
#   pivot_wider(names_from=x, values_from=number) %>% 
#   mutate(year = str_sub(year, start=2, end=5))
```

# 6.

Scrape a table of your choice from Wikipedia. Try to pick a simple table with one header, unless you are feeling up for a challenge.  Be sure to print out the table for the grader to see. 

```{r}

```

