---
title: "Homework H"
subtitle: '`forcats`: working with categorical data'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(forcats)

#LOAD DATASET
# This diamonds dataset is built into the tidyverse package
data("gss_cat")
```

Today's dataset, `gss_cat`, is a sample of data from the General Social Survey, a long-running US survey conducted by the independent research organization NORC at the University of Chicago. The survey has thousands of questions, but `gss_cat` only contains the 9 variables.   

Begin by reading more about each variable in the dataset by typing `?gss_cat` into the console. 

# 1.  
For each categorical/factor variable in `gss_cat` identify whether the order of the levels is ordinal or nominal. 

marital - 
race - 
rincome - 
partyid - 
relig - 
denom - 


# 2. 
What are the levels of the variable `partyid`? Create a table which displays how many people are in each category of `partyid`. 

```{r}

```

# 3. 
Construct a barplot which displays `partyid` on the x-axis and the the height of the bars represents the count of how many people fall in each category. What makes the default bar chart hard to understand? 

```{r}

```

# 4.
Regroup `partyid` variable to only contain four groups: "rep", "ind", "dem", and "other". Recreate the barchart above with your improved groupings. 

```{r}

```

# 5.
What are the levels of the `relig` variable? Create a table which counts how many people belong to each religion. Be sure to print out your table is a pretty way using the `kableExtra` package. 

```{r}

```

# 6. 
Create a new variable in the dataset called `top_relig` which only contains the 5 most popular religions and all other categories are grouped into an "other category". Create table which counts the number of people in each `top_relig` category. Be sure to print out your table is a pretty way using the `xtable` package.  

```{r}

```

# 7. 
Explore the relationship between marital status and the number of TV hours watched. Your results should include an appropriate plot that is well-labelled. Pay attention to the ordering of any categorical variables in your plot to ensure they are ordered in an appropriate way. 

```{r}

```


# 8.
Explore the relationship between one of the categorical variables in this dataset over time. Your results should include an appropriate plot  that is well-labelled. Pay attention to the ordering of any categorical variables in your plot to ensure they are ordered in an appropriate way. 

```{r}

```


