---
title: "STAT 118: Homework K"
subtitle: 'Intro to Maps'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(sf) #this is a package needed so R can work with sf objects
library(maps)
```

# Using the `maps` package

# 1.
Use the `maps` package to create a map of New Zealand. To access map data for New Zealand use the code: `nz_maps <- map_data("world", region = "New Zealand")`. You may need to subset the latitude and longitude coordinates to get a great map of New Zealand. The land should be some shade of orange. 

```{r}

```


# Use the `sf` package

```{r}
#LOAD DATA
library(spData) #this packages contains the dataset (with sf objects) that we will be using today
data("nz")
data("us_states")
data("us_counties")
```

# 2.
Use the `sf` package to create a map of New Zealand. To access `sf` geometries for New Zealand use the "nz" dataset loaded above. The land should be some shade of orange. 

```{r}

```

# 3.
Name two differences between the two New Zealand maps you created above. 

# 4. 
Use the `us_states` dataset from above to create a map of the US States. All the land map should be some shade of red. 

```{r}

```

# 5. 
The `us_states` dataset has a column `REGION` which indicates whether the state is "Northeast", "Midwest", "South", or "West". Create a map which shades each state depending on the REGION it is located in.  

```{r}
 
```

# 6.
Create a cloropleth map which colors each state depending on the total population of that state in 2015 (`total_pop_15` column in the `us_states` dataset). 

```{r}

```

Suppose we wish to incorporate data from another source on each state. This will require us to join the `sf` data with another dataset (remember joins from before?). 

```{r}
#dataset which contains information about each state
data(state) 
state_data <- data.frame(state.x77)
#weirdly, the state names are listed as row names instead of in their own column. The below code fixes this. 
state_data$NAME <- rownames(state_data)
```

# 7. 
Join together the `state_data` dataset with the `sf` data housed in `us_states` into a new dataset called `states_map_data`. The key variable is the state name. 

```{r}

```

# 8. 
Note that in the previous step we lost one data row. What was it? 

# 9. 
Ignoring the fact that we lost one row, use your new dataset `states_map_data` (from 7) to create a cloropleth map which colors each state depending on the illiteracy rate in 1970 as a percent of the population (`Illiteracy`). Use any color palette you like. 