---
title: "STAT 118: Homework F"
subtitle: "Customizing Plots: `scales`, labels, `facet_wrap()`"
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r}
# load packages
library(tidyverse)

# load data
library(gapminder)
```

# 1. Gapminder Scatterplot

- For the year 2007, plot GDP per capita (x-axis) vs. life expectancy (y-axis).
- Format large numbers as numbers with commas (not scientific notation)
- color points by continent
- Be sure your axes are clearly labelled for a general audience

```{r}

```


# 2. Log-Transformed Gapminder Scatterplot

Take your scatterplot from the previous problem. Log-transform the GDP per capita axis. Explain why a log-transformed x-axis is useful here. 

```{r}

```

# 3. Gapminder Scatterplot with labels

Take your scatterplot from the previous problem. Use `geom_text_repel()` to label the subset of countres which have a GDP per capita over over $40,000. 

```{r}

```


# 4. Gapminder Scatterplot over the years

Repeat this plot for all years in the dataset. Hint: you'll need to make sure you are using the full dataset for all years (not just 2007 like in the previous plots) AND you can use a nifty function that we talked about to repeat the analysis for all years in only one line of code! 

```{r}

```

# 5. Gapminder US Time Series

- Create a time-series line plot for GDP per capita in the United States
- Label the highest and lowest years using geom_text_repel(). 
- Be sure that the axis showing the GDP per capita is shown in currency format (with dollar signs!)
- Be sure your axes are clearly labelled for a general audience

```{r}

```

# 6. Explain using Gapminder US Time Series

How has GDP per capita in the U.S. changed over time? What major historical events might explain large shifts?



