---
title: "STAT 118: Homework R"
subtitle: 'Lubridate'
author: "YOUR NAME HERE"
format:
  html: 
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(lubridate)

#LOAD DATA
library(nycflights13)
data("flights")
```


# 1.
Create a new column in the flights dataset called `departure_datetime` which displays the departure datetime (for example, 2013-01-01 05:15:00)

```{r}

```


# 2. 
Create a new column in the flights dataset called  `sched_departure_datetime` which displays the scheduled departure datetime (for example, 2013-01-01 05:15:00)

```{r}

```

# 3.
Use an appropriate function to calculate the difference, in minutes, between the scheduled departure and the actual departure time. Save your results in a new column called `calc_dep_delay`. Note that your new column `calc_dep_delay` should have the same values as `dep_delay`.  

```{r}

```


# 4.
Create a new column called `overnight` which displays a 1 if the flights is overnight and 0 if the flight is not overnight. Hint: If the flight is overnight, the arrival time will be before the departure time. 

```{r}

```



# 5. 

Block time is defined as the time between departure and arrival time. Fun fact: pilots and flight attendents are only paid for block time, and that doesn't include boarding. Block time includes:

- some time spent on the ground at the origin (doing safety checks, taxiing from the gate to the runway, waiting to get cleared to takeoff, etc.) 
- the amount of time in the air 
- some time spent on the ground at the destination (taxiing from the runway to the gate, etc.)

Calculate a new column called `block_time` which is calculated by taking the `arrival_datetime` and subtracting the `departure_daterime`. 

```{r}

```

#6. 

Calculate a new column called `ground_time` which is calculated by taking the `block_time` and subtracting the `airtime`. Note that `airtime` is given in minutes and your calculated `ground_time` should also be given in minutes. 

```{r}

```


