---
title: 'MATH 118: Notes P'
subtitle: 'Lubridate'
output:
  html_document:
    code_folding: hide
  pdf_document: default
---

```{r}
#LOAD PACKAGES 
library(tidyverse)
library(lubridate)

#LOAD DATA
friendsvisits <- read.csv("data/friendsvisits.csv")
# In short, this made-up dataset contains information about the times that our host(s) had friends over and the times that they left.
```

# Date Formats

Think of how many different formats you know of to list today's date: 



Yikes! 

# Date, Time, and Datetime

Date/time data are data that conveys information about, you guessed it, date and/or time! There are three relevant data types when we talk about date/time data:

1. Date - only has the date (e.g. 2020-05-15) 
2. Time - only has the time (e.g. 20:45:00) 
3. Datetime - has both the date and time (e.g. 2020-05-15 20:45:00)

# Standard Date Format

The `ymd()` function transforms data in all kinds of different formats into a standardized date format displaying year, then month, then day. 

```{r}
ymd("06 02 04")
ymd("06/02/04")
ymd("20060204")  # works as well
ymd("2006 2 4")
ymd(060204)  # works with numbers
```

`mdy()` (month day year) and `dmy()` (day month year) formats also exist. 

```{r}
ymd_hms("2020-04-01 10:30:13")
ymd_hm("2020/04/01 10.30")
```

# Making Dates From Values

```{r}
make_date(year = 2020, month = 7, day = 13)

make_datetime(year = 2020, month = 7, day = 13, hour = 8, min=30)
```

Unfortunately, because the information about datetime is divided up into different columns, R does not recognize it as date/time data. What we need to do is combine and convert all of these columns into datetime. To do this, we can use the function `make_datetime()`

```{r}

```

How can we turn values like 1951 into 19:51:00? Once again, `make_datetime()` is the answer!

```{r}
#%% indicates x mod y and %/% indicates integer division.
# %% indicates 830 mod 100 = 8
# %/% indicates the remainder of 830 mod 100 = 30


```


# Working with Time Spans

```{r}

```


# Rounding Times

```{r}
t <- ymd_hms("2022-11-15 00:08:30")
```

```{r}
#Round
round_date(t, unit = "second") #no change
round_date(t, unit = "minute")
round_date(t, unit = "hour")
round_date(t, unit = "day")
```


```{r}
#Force Round UP
ceiling_date(t, unit = "minute")
ceiling_date(t, unit = "hour")
```

```{r}
#Force Round DOWN
floor_date(t, unit = "minute")
floor_date(t, unit = "hour")
```




