---
title: "MATH 118: Homework O"
subtitle: 'Maps'
output:
  html_document:
    code_folding: hide
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(sf) 
library(leaflet)
library(spData)
```

Choose one of the datasets provided which displays the latitude and longitude of many locations. Your job will be to create a map which displays the locations of the items on an appropriate map.

1. Use the space below to import in your dataset of choice (choices are on the Canvas Assignment page). 

**Keep in mind that you may want to work with ALL locations in the dataset OR you may wish to work with a subset of the locations -- totally your choice.**

```{r}
dunkin <- read.csv("~/Library/CloudStorage/OneDrive-MiddleburyCollege/MATH0118 - Fall 2022/dunkin_stores.csv")
```

2. Find an appropriate `sf` dataset for the locations of your data. Recall the `spData` package contains many different `sf` objects, so you might be able to find an appropriate map there. 

```{r}
data(
"us_states"
)
```

3. Create an `ggplot` map (using `sf` objects) which displays the locations from your dataset as points on the map. All points should be the same size (choose an appropriate size and color). Your plot should include a title and appropriate colors. 

```{r}
us_states %>%
ggplot() +
geom_sf() +
theme_light()
```

4. Create an `ggplot` map (using `sf` objects) which displays the locations from your dataset as points on the map. Your points should vary in size depending on a quantitative variable in your data OR vary in color depending on a categorical variable in your data. Your plot should include a title and appropriate colors.

```{r}
us_states %>%  
ggplot() +  
  geom_sf() + 
  geom_point(data=dunkin_stores, aes(x=loc_long, y=loc_lat), pch=19, size=1) +
   coord_sf(xlim = c(-125, -65), 
           ylim = c(20, 50))+
  xlab("Longitude")+
  ylab('Latitude')
```

5. Create a `leaflet` map which displays the locations from your dataset as well-labeled markers on a map. 

```{r}

```

