---
title: "Homework E"
subtitle: "More making plots  with `ggplot2`"
author: "YOUR NAME HERE"
format:
  html:
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
execute: 
  warning: FALSE
  message: FALSE
---

```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)

#Load Penguins Data
library(palmerpenguins)
data("penguins")

#Load Iris Data
data("iris")

# Load gapminder Data
library(gapminder)
data("gapminder")
```

Reproduce the graphs as best as you can -- images of the graphs are available on the assignment page on Canvas. Focus your efforts on getting the content correct. If you have time at the end, as a bonus, you can try to match the styling as closely as you can. 

1. penguins scatterplot

```{r}

```

2. iris boxplot

```{r}

```

3. gapminder line chart

```{r}

```

4. mpg bar chart

```{r}

```

5. penguins facet wrap

```{r}

```

6. gapminder labels -- hint: the labels comes from using `geom_label_repel()` in the `ggrepel` package. It may be quite a challenge to label the 5 countries. It is okay to just label one of the countries. 

```{r}

```


