---
title: "Homework H"
subtitle: "`forcats`: for working with categorical variables"
author: "YOUR NAME HERE"
format:
  html:
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
execute: 
  warning: FALSE
  message: FALSE
---

```{r}
#LOAD PACKAGES 
library(tidyverse)
library(forcats)

#LOAD DATA
portal_rodent <- read.csv("https://github.com/weecology/PortalData/raw/main/Rodents/Portal_rodent.csv")
portal_species <- read.csv("https://raw.githubusercontent.com/weecology/PortalData/main/Rodents/Portal_rodent_species.csv")
```

1.  Choose 3 different species of rodents. You may want to choose 3 from the same genus or from 3 different genera for comparison. Create a dataset called `my_rodents` which has all the data on any rodents of your species of choice caught in Portal, AZ. You should display the time the rodents were captured (year, month, day), the species scientific and common name, and the sex and pregnancy status. 

```{r}

```


2. Create a table which displays how many rodents are of each species (or commonname) were recorded over the period of study. Be sure that it's broken down by sex. 

```{r}

```

3. Construct an appropriate plot to display the data above. Be sure information about species (or commonname), sex, and count is all displayed in your plot & that your plot is pretty and nicely labeled. 

```{r}

```

4. What is the order of the levels of species (or commonname) displayed in your chart?  



5. Reorder your the factor for species (or commonname) from highest total number caught (regardless of sex) to lowest total number caught. You might need to do some extra work separate to figure out what this order is. 

```{r}

```

6. Sex is ordered in alphabetically. Reorder sex so that it displays males first and then females. 

```{r}

```


7. Reconstruct your appropriate plot from 3. Be sure the ordering you created in 5 and 6 carries through into your plot. 

```{r}

```

7. Of the female rodents of each species, what number were captured pregnant? What number were captured when they were not pregnant? Make a nice well-labelled table that is well-labelled including "not pregnant" or something similar. 

```{r}

```






