---
title: "Homework I"
subtitle: "`lubridate"
author: "YOUR NAME HERE"
format:
  html:
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
execute: 
  warning: FALSE
  message: FALSE
---

There is a lubridate cheatsheet here: https://lubridate.tidyverse.org/


```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
library(lubridate)

# LOAD DATA. You can  read about the descriptions of the columns here: https://www.ndbc.noaa.gov/station_realtime.php?station=bgxn3
# Data from National Estuarine Research Reserve System (43.059 N 70.830 W 43°3'32" N 70°49'49" W)

download.file(url='https://www.ndbc.noaa.gov/data/realtime2/BGXN3.txt',
              destfile = 'greatbay.txt')

write.csv(x = read.csv(file = 'greatbay.txt', header = TRUE, sep='')[-1,],file = 'greatbay.txt', quote=FALSE, row.names = FALSE)

greatbay <- read.csv(file = 'greatbay.txt', header = TRUE)

```


1. Use `lubridate` to make a new column a datetime object (for example, 2013-01-01 05:15). 

```{r}


```


2. The above datetime object is in GMT. Convert the datetime object from GMT to EST to be on the right time zone. Hint: You can use the `with_tz()` function 

```{r}

```

3. Use an appropriate function to calculate the difference, in minutes, between the current time and the datetime (EST) in the dataset. Build a new column and save this calculated difference. Hint: You can use `Sys.time()` to get the current time on your computer.

```{r}

```


4. Build a plot of Air temperature (Celsius) (ATMP) over time. Make it both a scatter plot with lines connecting the points.

```{r}



```


5. Now rebuild the above plot, but take the mean ATMP per day before plotting. There are multiple ways to accomplish this task.

```{r}



```

6. Build a plot of any two variables (or more!) that you find interesting. Write a few sentences of what you find. 

```{r}


```
