---
title: "Notes P"
subtitle: "Pretty Documents: Colors, Themes, and Scales"
format:
  html:
    toc: true
    code-overflow: wrap
    code-fold: false
    embed-resources: true
execute: 
  message: FALSE
  warning: FALSE
---

```{r}
#LOAD PACKAGES
library(tidyverse)
```

# Themes

If you want to set your ggplot theme globally (for the whole document) you can use this code: 

```{r}
theme_set(theme_minimal())
```

# Colors

## Default Colors

```{r}
#| layout-ncol: 2
#| fig-cap: "Default Colors"
#| fig-subcap: 
#|   - "Boxplot Plot -- discrete colors"
#|   - "Scatterplot -- continuous colors"
#| fig-cap-location: top
bp <- ggplot(iris, aes(Species, Sepal.Length)) + 
  geom_boxplot(aes(fill = Species)) +
  theme_minimal() +
  theme(legend.position = "top")
bp

# Scatter plot
sp <- ggplot(iris, aes(Sepal.Length, Sepal.Width)) + 
  geom_point(aes(color = Petal.Length)) +
  theme_minimal()+
  theme(legend.position = "top")
sp
```

## On a plot

For a plot you can create a custom color palette: 

|  | color | fill  |
|---|---|---|
|  | This will be applied to points, lines and texts | This will change the fill color of areas, such as in box plot, bar plot, histogram, density plots, etc. |
| discrete | `scale_color_manual` | `scale_fill_manual` |
| continuous | `scale_color_gradient` | `scale_fill_gradient` |
| want continuous from discrete scale | `scale_color_distill` | `scale_fill_distill` |


```{r}
#| layout-ncol: 2
#| layout-nrow: 2

bp

bp + 
  scale_fill_manual(values=c("#9966cc", "#005bac", "#d50032"))

sp 

sp +
  scale_colour_gradient(low = "yellow", high = "red")
```



## Color Palettes: `colorBrewer`

The RColorBrewer package creates a nice looking color palettes. 

```{r}
#| fig-height: 10
library(RColorBrewer)
display.brewer.all()
```


- **Sequential palettes** (first list of colors), which are suited to ordered data that progress from low to high (gradient). The palettes names are : Blues, BuGn, BuPu, GnBu, Greens, Greys, Oranges, OrRd, PuBu, PuBuGn, PuRd, Purples, RdPu, Reds, YlGn, YlGnBu YlOrBr, YlOrRd.
- **Qualitative palettes** (second list of colors), which are best suited to represent nominal or categorical data. They not imply magnitude differences between groups. The palettes names are : Accent, Dark2, Paired, Pastel1, Pastel2, Set1, Set2, Set3.
- **Diverging palettes** (third list of colors), which put equal emphasis on mid-range critical values and extremes at both ends of the data range. The diverging palettes are : BrBG, PiYG, PRGn, PuOr, RdBu, RdGy, RdYlBu, RdYlGn, Spectral

```{r}
#| layout-ncol: 2
#| layout-nrow: 2

bp

bp + 
  scale_fill_brewer(palette = "Dark2")

sp 

sp +
  scale_color_distiller(palette = "BuPu")
```

## Other Cool Palettes

- `ggsci`
- `wesanderson`
- `tayloRswift`

# Global Custom Color Palettes 

If you want to set your ggplot colors globally (for the whole document) you can use this code: 

```{r}
options(ggplot2.discrete.color= c("#9966cc", "#005bac", "#d50032", "#c9b037", "#3D424D"), 
        ggplot2.discrete.fill = c("#9966cc", "#005bac", "#d50032", "#c9b037", "#3D424D"))
```


# Legends


##  hide the legend

```{r}
#| layout-ncol: 2
bp


bp + 
  guides(fill="none")
```

## customizing title of legend

```{r}
#| layout-ncol: 2
sp

sp + 
  scale_color_continuous(name="Petal Length")
 
```


# Axes and scales

## customizing axes breaks

```{r}
#| layout-ncol: 2
sp

sp + 
  scale_y_continuous(breaks=c(2,3,4,5))
```

