---
title: 'Notes C'
subtitle: 'Aggregating data with `summarize()`, `group_by()`'
author: "EMW"
date: "Tues, Jun 4, 2024"
format:
  html:
    toc: true
    code-overflow: wrap
    code-fold: false
    embed-resources: true
execute: 
  message: FALSE
  warning: FALSE
---


```{r message=FALSE, warning=FALSE}
#LOAD PACKAGES 
library(tidyverse)
```

Today's Dataset: `palmerpenguins`
Size measurements, clutch observations, and blood isotope ratios for adult foraging Adélie, Chinstrap, and Gentoo penguins observed on islands in the Palmer Archipelago near Palmer Station, Antarctica. Data were collected and made available by Dr. Kristen Gorman and the Palmer Station Long Term Ecological Research (LTER) Program.

```{r message=FALSE, warning=FALSE}
#LOAD DATA 
library(palmerpenguins)
data(penguins)
```


# Clean up the data to remove rows with missing data

```{r}
penguins <- penguins %>%
  drop_na()
#sometimes this is appropriate...
#sometimes dropping missing values might introduce bias into the study
```

# `summarize` Function or `summarise` Function (either works)

Suppose we are interested in the average/mean bill length of all Adelie penguins: 

```{r}
penguins %>% 
  filter(species == "Adelie") %>% 
  summarize(Mean_bill_length = mean(bill_length_mm),
            Mean_bill_depth = mean(bill_depth_mm))
```

Suppose we are interested in the average bill length AND average bill depth of all Adelie penguins: 

```{r}
penguins %>% 
  filter(species == "Adelie") %>% 
  summarize(Mean_bill_length = mean(bill_length_mm))
```

There are lots of other functions available: 

- `min`: minimum value
- `max`: maximum value
- `mean`: average or mean value
- `median`: median value
- `var`: variance 
- `sd`: standard deviation 
- `n`: count or number of values
- `n_distinct`: counts number of distinct values

Suppose we are interested in the average bill length AND the median bill length of all Adelie penguins: 

```{r}
penguins %>% 
  filter(species == "Adelie") %>% 
  summarize(mean_bill_length_mm = mean(bill_length_mm), 
              median_bill_length = median(bill_length_mm))

```

# `group_by`

Let's say we were interested in the average bill length and bill depth of all penguin species in this dataset. We could repeat this for the other species (Gentoo and Chinstrap). This would be a fair amount of work AND the results would not end up in the same table. 


```{r}
penguins %>% 
  group_by(species) %>%  
  summarize(Mean_bill_length = mean(bill_length_mm),
            Mean_bill_depth = mean(bill_depth_mm))

```

## Multiple Groups

Suppose we want the average bill length and average bill depth broken down by both species and sex: 

```{r}
penguins %>% 
  group_by(species, sex) %>%  
  summarize(Mean_bill_length = mean(bill_length_mm),
            Mean_bill_depth = mean(bill_depth_mm))

penguins %>% 
  group_by(sex, species) %>%  
  summarize(Mean_bill_length = mean(bill_length_mm),
            Mean_bill_depth = mean(bill_depth_mm))

```

# More Practice

Suppose we want to calculate the number of distinct islands each species is found on:

```{r}
penguins %>% 
  group_by(species) %>% 
  summarize(no_distinct_islands = n_distinct(island))
```

Suppose we are interested in how many penguins of each species are on each island in the year 2007 (with measurement data available): 

```{r}
penguins %>% 
  filter(year == 2007) %>% 
  group_by(species, island) %>% 
  summarize(count=n())
  
```

