---
title: "Homework K"
subtitle: "Sustainability Data"
author: "YOUR NAME HERE"
format:
  html:
    toc: true
    code-overflow: wrap
    code-fold: true
    embed-resources: true
execute: 
  warning: FALSE
  message: FALSE
---




```{r }
#| eval: FALSE

#LOAD PACKAGES 
library(tidyverse)
library(lubridate)

# LOAD DATA
power <- read.csv("../data/power.csv")
```


0. use the SML Data Dashboard to recreate a dataset for 2024. (Wind Power and Wind Speed)


1. Use `lubridate` the date column a date data type. 

```{r}


```

2. Use tables and/or text to provide some background on the data. How many data points are there? Over what time frame? What are the means and ranges of some key parameters?

```{r}

```

3. Build a plot of daily power generation of solar and wind over the 2024 season so far.  Comment on the trends.  

```{r}

```

4. Build a plot of power generated so far in 2024 over time? How does the amount compare to the amount produced in the first part of 2023? Comment on the trends.  

```{r}

```


5. Build a plot of any two variables (or more!) that you find interesting. Write a few sentences of what you find. 

```{r}


```
